Binocular combination in the autonomic nervous system

### 2025-09-15 manuscript.Rmd
Changes

pdf(paste0(figdir,"methodsfigrods1.pdf"), bg="transparent", height = 13, width = 12)

@@

@@

filt <- butter(3,0.083)
filtwaveP <- signal::filter(filt, meanwavesP)
filtU <- signal::filter(filt,meanwavesPCI[1,])
filtL <- signal::filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.3),border=NA)
lines(times, filtwaveP, col=colpal[2], lwd=1.5)
lines(times, (sinewave/10)-0.9, col='black', lwd=2)

@@

@@

@@

@@

>>>>

pdf(paste0(figdir,"methodsfigrods.pdf"), bg="transparent", height = 13, width = 12)

@@

prefixlist <- c('P6','P7','P3','P5')

  d <- dir(datadir,pattern=prefixlist[1], full.names = TRUE)

@@

filt <- butter(3,0.083)
filtwaveP <- signal::filter(filt, meanwavesP)
filtU <- signal::filter(filt,meanwavesPCI[1,])
filtL <- signal::filter(filt,meanwavesPCI[2,])
polygon(times[c(1:length(times),length(times):1)],c(filtL,filtU[length(filtU):1]),col=addalpha(colpal[2],0.4),border=NA)
lines(times, filtwaveP, col=colpal[2], lwd=1.5)
lines(times, (sinewave/10)-0.9, col='black', lwd=2)

for (part in 1:24) {
  load(file=paste0(d[part]))
  filt <- butter(3,0.083)
  filtwaveP <- signal::filter(filt, meanwavesP)
  lines(times, filtwaveP, col=addalpha(colpal[2],0.7), lwd=0.2)
}

@@

  load(file=paste0(datadir,'AveragedataLM.RData'))
d <- dir(datadir,pattern=prefixlist[2], full.names = TRUE)

@@

  load(file=paste0(datadir,'AveragedataS.RData'))
  d <- dir(datadir,pattern=prefixlist[3], full.names = TRUE)

@@

load(file=paste0(datadir,'AveragedataMel.RData'))
d <- dir(datadir,pattern=prefixlist[4], full.names = TRUE)

@@

```{r individualpupiltraces, include=FALSE, results='hide'}

pdf(paste0(figdir,"indpupiltrace.pdf"), bg="transparent", height = 13, width = 12)

layout(matrix(1:4, 2, 2, byrow = TRUE))
par(mar=c(3.5,2.5,1,1))

prefixlist <- c('P6','P7','P3','P5')

  d <- dir(datadir,pattern=prefixlist[1], full.names = TRUE)

lines(times, (sinewave/10)-0.9, col='black', lwd=2)

for (part in 1:24) {
  load(file=paste0(d[part]))
  filt <- butter(3,0.083)
  filtwaveP <- signal::filter(filt, meanwavesP)
  lines(times, filtwaveP, col=colpal[2], lwd=1)
}

text(-1,0.4,'(a)',pos=4,cex=2)

d <- dir(datadir,pattern=prefixlist[2], full.names = TRUE)

lines(times, (sinewave/10)-0.9, col='black', lwd=2)

for (part in 1:24) {
  load(file=paste0(d[part]))
  filt <- butter(3,0.083)
  filtwaveP <- signal::filter(filt, meanwavesP)
  lines(times, filtwaveP, col=colpal[2], lwd=1)
}

text(-1,0.4,'(b)',pos=4,cex=2)

  d <- dir(datadir,pattern=prefixlist[3], full.names = TRUE)

lines(times, (sinewave/10)-0.9, col='black', lwd=2)

for (part in 1:24) {
  load(file=paste0(d[part]))
  filt <- butter(3,0.083)
  filtwaveP <- signal::filter(filt, meanwavesP)
  lines(times, filtwaveP, col=colpal[2], lwd=1)
}

text(-1,0.4,'(c)',pos=4,cex=2)

d <- dir(datadir,pattern=prefixlist[4], full.names = TRUE)

lines(times, (sinewave/10)-0.9, col='black', lwd=2)

for (part in 1:24) {
  load(file=paste0(d[part]))
  filt <- butter(3,0.083)
  filtwaveP <- signal::filter(filt, meanwavesP)
  lines(times, filtwaveP, col=colpal[2], lwd=1)
}

text(-1,0.4,'(d)',pos=4,cex=2)
